---
title: "Prepare data for Jenn and Mathilde Manual Acoustic Analysis"
output: html_document
date: "2022-11-21"
---

```{r setup, echo = F}

knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(tidy = "styler")
 

getwd()

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
#renv::install("rstudio/renv")
library(renv)
library(stringr)
```

# Extract raw bat acoustic data for manual acoustic analysis for Jenn Fairchild's manual acoustic analysis
1.a - Read id.csv files from all WAV folder directories of the bat acoustic data from the Follo Forest 2021 and 2022 field seasons 
1.b - Combine those id.csv's into one master csv file
2.a - Subset to only include files that correspond to AUTO.ID.s of PIPY, PIPI, PINA, NoID, NYNO (Jenn) -J1 
2.b - Subset to only include Myotis and Plecotus species as well as BABA (Mathilde) - M1 
3.a - Subset J1 to only include data between May 15 and 27 June for both seasons  - J2 
3.b - Subset M1 to only include the data from 2022 (whole season) - M2
4.a - Copy files that match J2 into the external hard disk 
4.b - Copy files that match M2 into the Project Largefile. 

## 2021 FIRST
Step 1 - read the csv files of all bat acoustic data for both Follo Forest seasons and combine them 
```{r}

## 2021 
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021"))) 
#also includes 2022 data)
getwd()
#"\\\\largefile.nmbu.no/Project/FolloForest2021" This also uncludes 2022 data (sorry that is confusing)

# Specify directories
# 2021 field season first (data structures slightly different between seasons)


# folders where csv files are all in for each site
inputFF1_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF1" 

inputFF2_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF2" 

inputFF3_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF3" 

inputFF4_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF4" 

inputFF5_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF5" 

inputFF6_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF6" 

inputFF7_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF7" 

inputFF8_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF8" 

inputFF9_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF9" 

inputFF10_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF10" 

inputFF11_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF11"

inputFF12_21 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF12"


output21 <-"//largefile.nmbu.no/Project/FolloForest2021/Processed_Data/Bat Acoustic Data/RSummary_2022" # where you want to save your data
name   <-"FF21AutoClass.csv"



#To set the path to your csv files
#To grab and list all your csv files
#my_files <- list.files(path=path, pattern="*.txt")

# It can take a while to load each set of csv files so I find the beepr package helpful here... 

FF1<- list.files(path=inputFF1_21, pattern="id.csv", recursive = TRUE)
beep() 

FF2<- list.files(path=inputFF2_21, pattern="id.csv", recursive = TRUE)
beep() 

FF3<- list.files(path=inputFF3_21, pattern="id.csv", recursive = TRUE)
beep()

FF4<- list.files(path=inputFF4_21, pattern="id.csv", recursive = TRUE)
beep()

FF5<- list.files(path=inputFF5_21, pattern="id.csv", recursive = TRUE)
beep()

FF6<- list.files(path=inputFF6_21, pattern="id.csv", recursive = TRUE)
beep()

FF7<- list.files(path=inputFF7_21, pattern="id.csv", recursive = TRUE)
beep()

FF8<- list.files(path=inputFF8_21, pattern="id.csv", recursive = TRUE)
beep()

FF9<- list.files(path=inputFF9_21, pattern="id.csv", recursive = TRUE)
#beep()

FF10<- list.files(path=inputFF10_21, pattern="id.csv", recursive = TRUE)
#beep()

FF11<- list.files(path=inputFF11_21, pattern="id.csv", recursive = TRUE)
#beep()

FF12<- list.files(path=inputFF12_21, pattern="id.csv", recursive = TRUE)
#beep()

getwd()
# "\\\\largefile.nmbu.no/Project/FolloForest2021"
FF1
# [1] "FF1-CB/WAV_FF1-CB_06.09.2021_A/id.csv" "FF1-CB/WAV_FF1-CB_06.09.2021_B/id.csv" ...
# Slight gap between these so I need to manually reset the root directory for every site:( )


# #To read all your csv files and create a list with all these elements

## FF01
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF1")))
getwd()

FF01_data <- lapply(FF1, read.csv)

## FF02
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF2")))
getwd()

 FF02_data <- lapply(FF2, read.csv)

 ## FF03 
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF3")))
getwd()

 FF03_data <- lapply(FF3, read.csv)

 ## FF04
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF4")))
getwd()

 FF04_data <- lapply(FF4, read.csv)
 
## FF05
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF5")))
getwd()

 FF05_data <- lapply(FF5, read.csv)
 
## FF06
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF6")))
getwd()

 FF06_data <- lapply(FF6, read.csv)
 
## FF07
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF7")))
getwd()

 FF07_data <- lapply(FF7, read.csv)

 ## FF08
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF8")))
getwd() 

  FF08_data <- lapply(FF8, read.csv)

 ## FF09
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF9")))
getwd() 
 
  FF09_data <- lapply(FF9, read.csv)

 ## FF10
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF10")))
getwd() 

   FF10_data <- lapply(FF10, read.csv)

  ## FF11
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF11")))
getwd()   
   
 FF11_data <- lapply(FF11, read.csv)

  ## FF12
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF12")))
getwd()   
 
  FF12_data <- lapply(FF12, read.csv)
# 
  
#To add the name of each csv in the list
names(FF01_data) <- gsub("//.csv$", "", FF1)
names(FF02_data) <- gsub("//.csv$", "", FF2)
names(FF03_data) <- gsub("//.csv$", "", FF3)
names(FF04_data) <- gsub("//.csv$", "", FF4)
names(FF05_data) <- gsub("//.csv$", "", FF5)
names(FF06_data) <- gsub("//.csv$", "", FF6)
names(FF07_data) <- gsub("//.csv$", "", FF7)
names(FF08_data) <- gsub("//.csv$", "", FF8)
names(FF09_data) <- gsub("//.csv$", "", FF9)
names(FF10_data) <- gsub("//.csv$", "", FF10)
names(FF11_data) <- gsub("//.csv$", "", FF11)
names(FF12_data) <- gsub("//.csv$", "", FF12)


#To create one single dataframe with all single dataframes
big_FF01<- rbindlist(FF01_data, fill = TRUE)
big_FF02<- rbindlist(FF02_data, fill = TRUE)
big_FF03<- rbindlist(FF03_data, fill = TRUE)
big_FF04<- rbindlist(FF04_data, fill = TRUE)
big_FF05<- rbindlist(FF05_data, fill = TRUE)
big_FF06<- rbindlist(FF06_data, fill = TRUE)
big_FF07<- rbindlist(FF07_data, fill = TRUE)
big_FF08<- rbindlist(FF08_data, fill = TRUE)
big_FF09<- rbindlist(FF09_data, fill = TRUE)
big_FF10<- rbindlist(FF10_data, fill = TRUE)
big_FF11<- rbindlist(FF11_data, fill = TRUE)
big_FF12<- rbindlist(FF12_data, fill = TRUE)


alist = list(big_FF01, big_FF02, big_FF03, big_FF04, big_FF05, big_FF06, big_FF07, big_FF08, big_FF09, big_FF10, big_FF11, big_FF12)

big_data <- rbindlist(alist, fill=TRUE)

setwd("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/RSummary_2022")

getwd()

#write.csv(big_data, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_unedited.csv")


# Explore where the NAs are coming from... 

big_data$AUTO.ID. <- as.factor(big_data$AUTO.ID.)
summary(big_data$AUTO.ID.)

# BARBAR EPTNIL EPTSER MYOALC MYOBEC MYOBRA MYODAS MYODAU MYOMYO MYOMYS MYONAT NYCLEI NYCNOC   NoID  Noise 
#   1706  83010   3122    124    159   8535   2383  12718     64   7038    261    779   2783  54270 261602 
# PIPNAT PIPPIP PIPPYG PLEAUR PLEAUS VESMUR   NA's 
#   1764   2387  38252   1318   1542    123    364 

big_FF04$AUTO.ID. <- as.factor(big_FF04$AUTO.ID.)
summary(big_FF04$AUTO.ID.) # 355 NAs from this site... mostly from the CB detector is seems... perhaps there was some issues with the microphone that resolved themselves.  
summary(big_FF04)
## I found another 8 NAs in FF-IB from the last day before the detector was collected. Could be there was a microphone failure or the detector had some other kind of issue. In any case, not much is lost and it does not appear to be a catastrophic failure. 

# In any case, it should be safe to remove these NAs. 
levels(big_data$AUTO.ID.)

big_data1 <- big_data %>% drop_na(AUTO.ID.) 
dim(big_data1)
# 483940     45
# 484304-483940 = 364 - GOOD!

# write.csv(big_data1, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA.csv")

# Remove the 261602 NOISE files as well. 

big_data2 <- big_data1 %>% filter(AUTO.ID. != "Noise") %>%  droplevels() 
summary(big_data2$AUTO.ID.)
dim(big_data2)
# 222338     45

#write.csv(big_data2, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise.csv")


```

# Step 2 - 2021
## 2021 data for Mathilde 
Mathilde probably won't use the 2021 dataset so I do not need to worry about this for now. 
```{r}
# # Grab all Plecotus species, Myotis species and Barbastelle observations. 
# 
# M1 <- big_data2 %>% filter(AUTO.ID. %in% c( "BARBAR", "MYOALC", "MYOBEC", "MYOBRA", "MYODAS", "MYODAU", "MYOMYO", "MYOMYS", "MYONAT", "PLEAUR", "PLEAUS", "NoID")) %>% droplevels
# dim(M1) # [1] 90118    45
# summary(M1)
# summary(M1$AUTO.ID.)
# # BARBAR MYOALC MYOBEC MYOBRA MYODAS MYODAU MYOMYO MYOMYS MYONAT   NoID PLEAUR PLEAUS 
# #   1706    124    159   8535   2383  12718     64   7038    261  54270   1318   1542 
# 
# #write.csv(M1, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_SRE_NoID_Only.csv")
# #M1 <- X2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_SRE_NoID_Only
# 
# ## EVENTUALLY ###
#  
# #Copy these files to a separate location.... 
```

# Step 3 - 2021 
## 2021 data for Jenn 

```{r}

J1 <- big_data2 
J1$date <- as.Date(J1$DATE)

# Filter to only include dates from 15.05 to 27.06 (least amount of equipment failures) 
# subset(temp, date> "2014-12-03" & date < "2014-12-05")
J1. <- subset(J1, date > "2021-05-14" & date < "2021-06-28")
dim(J1.) # [1] 65477    46
summary(J1.)
summary(J1.$AUTO.ID.)

# BARBAR EPTNIL EPTSER MYOALC MYOBEC MYOBRA MYODAS MYODAU MYOMYO MYOMYS MYONAT NYCLEI NYCNOC   NoID PIPNAT 
#    330  16919    730     44     54   3509    854   3359     23   3280    160    214   1145  20303   1455 
# PIPPIP PIPPYG PLEAUR PLEAUS VESMUR 
#    833  14737    168     35     57 

#write.csv(J1., "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_15-05_to_27_06.csv")
# Filter to only include MRE, NoID and Noctule species 


J2 <- J1. %>% filter(AUTO.ID. %in% c("NYCLEI", "NYCNOC", "NoID", "PIPNAT", "PIPPIP", "PIPPYG")) %>% droplevels() 

dim(J2) # [1] 38687    46
summary(J2$AUTO.ID.)
# NYCLEI NYCNOC   NoID PIPNAT PIPPIP PIPPYG 
#    214   1145  20303   1455    833  14737 

#write.csv(J2, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_MREandNoIDandNyctalus_15-05_to_27_06.csv")

J3 <- J2 %>% select(2:46)
#write.csv(J3, "id_2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_MREandNoIDandNyctalus_15-05_to_27_06.csv")
```


# Copy the 2021 files into a new directory 
# Starting wit Jenn's data 

```{r}
setwd("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/RSummary_2022")
# This next command will take forever to run - do not rerun it on accident! 

# Select all files with their complete file paths 
#mass_inventory <- list.files("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/", pattern = "000.wav", recursive = TRUE, all.files = FALSE, full.names = TRUE, ignore.case = FALSE) 

#write.csv(mass_inventory, "complete file path, all bat acoustic data Follo Forest2021.csv")

#mass_inventory <- complete_file_path_all_bat_acoustic_data_Follo_Forest2021 <- read_csv("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/RSummary_2022/complete file path, all bat acoustic data Follo Forest2021.csv")


mass_inventory_df <- as.data.frame(mass_inventory)
head(mass_inventory_df) # 484313 obs 
str(mass_inventory_df) # need to drop index column and rename mass_inventory column 
mass_inventory_df <- mass_inventory_df %>% select(-1) %>% rename(mass_inventory = x) 

mass_inventory_df$map <- mass_inventory_df$mass_inventory # make copy of the complete file paths column 
mass_inventory_df1 <- mass_inventory_df %>% filter(!str_detect(mass_inventory, "NOISE")) # Removed noise, now 225197 obs 

 
mass_inventory_df2 <- mass_inventory_df1 %>% mutate(map1 = str_remove(map, "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData//"))  
head(mass_inventory_df2$map1)

cols <- c("Site", "Plot", "Collection", "Data", "Data1", "file.name")
mass_inventory_df3 <- mass_inventory_df2 %>% tidyr::separate(col = map1, 
                                                             sep = "/",
                                                             into = cols, 
                                                             remove = FALSE) 
# parse out the file paths to just get the file names
# For some directories there were two "Data" folders (Data/Data) so I will need to recreate a complete file list from the two columns... 
summary(mass_inventory_df3)
# create a list now of only file names. 
filelist1 <- mass_inventory_df3 %>% select(Data1) # this column contains either "Data" or a file name
filelist1 <- subset(filelist1, Data1 != "Data") %>% rename(file.name = Data1) # 8728 obs 
filelist1_list <- list(filelist1)

filelist2 <- mass_inventory_df3 %>% select(file.name) %>% drop_na(file.name) # 216469

filelist2_list <- list(filelist2)

# the last column contains either a file name or "NA" for the columns that did not have Data folders

summary(filelist1)
summary(filelist2)  
# 216469 + 8728 = 225197 ## This is should be length of the final file list. 
filelist3 <- full_join(filelist1, filelist2)# 225197 obs, perfect!
#Now add this back as a column to the earlier dataset. 

mass_inventory_df4 <- mass_inventory_df3
mass_inventory_df4$filename <- filelist3$file.name 

#create a column that is easy to index with J2
J2_map <- J2 %>% select(OUT.FILE.FS) %>% rename(filename = OUT.FILE.FS)
J2_map_list <- list(J2_map$filename) # 38687 files

# subset the masss inventory to only include files that match what Jenn needs. 
str(mass_inventory_df4)
str(J2_map)
JennFilePaths <- inner_join(mass_inventory_df4, J2_map, by = "filename") 


# 38687 - 36162 = 2525 
# 2525 files missing for some reason.... 
# check for duplicates in the J2_map object
test <- duplicated(J2_map)
J2_map$filename[duplicated(J2_map$filename)] 
summary(test) # 2524 - looks like they are all duplicate files... 
# test to see if removing these also removes the NAs in the OUT FILE ZS issue... 

# J2 has 38687 observations
test1 <- J2 %>% distinct(OUT.FILE.FS) 
# test1 has 36163 observations
# 38687-36163 = 2524 
# There were a series of input directories assosciated with these NAs:
# FF6-OB_17.08.2021
# FF6-CB_17.08.2021
# FF6-IB_30.07.2021
# FF7-OB_13.07.2021
# FF7-IB_28.06.2021
# FF7-CB_28.06.2021
# FF6-OB_30.05.2021

# They all DO HAVE .000.wav files there, but for some reason a proportion of them are not recorded in the id.csvs assosciated with these data recoveries... for now I will have to ignore them but may extract entire datasets from these folders later if it looks like these 2000 ish observations are not just strange duplicates. 

my_files <- as.list(JennFilePaths$mass_inventory)
my_files_list <- unlist(my_files)# 36162 files 
head(my_files)
View(mass_inventory)

file.copy(from = my_files_list, 
          to = "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/ForJenn")

```


# 2022 
Combine all the bat acoustic data from 2022 

```{r}

## 2022
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics"))) 
#also includes 2022 data)
getwd()
#"\\\\largefile.nmbu.no/Project/FolloForest2021" This also uncludes 2022 data (sorry that is confusing)

# Specify directories
# 2021 field season first (data structures slightly different between seasons)


# folders where csv files are all in for each site
inputFF01_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF01" 

inputFF02_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF02"   

inputFF03_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF03" 

inputFF04_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF04" 

inputFF05_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF05" 

inputFF06_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF06" 

inputFF07_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF07"  

inputFF08_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF08"  

inputFF09_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF09" 

inputFF10_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF10" 

inputFF11_22 <-"//largefile.nmbu.no/Project/FolloForest2021/FolloForest2022/Acoustics/FF11" 


output21 <-"//largefile.nmbu.no/Project/FolloForest2021/Processed_Data/Bat Acoustic Data/RSummary_2022" # where you want to save your data
# name   <-"FF22AutoClass.csv"



#To set the path to your csv files
#To grab and list all your csv files
#my_files <- list.files(path=path, pattern="*.txt")

# It can take a while to load each set of csv files so I find the beepr package helpful here... 

FF1<- list.files(path=inputFF01_22, pattern="id.csv", recursive = TRUE)
#beep() 

FF2<- list.files(path=inputFF02_22, pattern="id.csv", recursive = TRUE)
#beep() 

FF3<- list.files(path=inputFF03_22, pattern="id.csv", recursive = TRUE)
#beep()

FF4<- list.files(path=inputFF04_22, pattern="id.csv", recursive = TRUE)
#beep()

FF5<- list.files(path=inputFF05_22, pattern="id.csv", recursive = TRUE)
#beep()

FF6<- list.files(path=inputFF06_22, pattern="id.csv", recursive = TRUE)
#beep()

FF7<- list.files(path=inputFF07_22, pattern="id.csv", recursive = TRUE)
#beep()

FF8<- list.files(path=inputFF08_22, pattern="id.csv", recursive = TRUE)
#beep()

FF9<- list.files(path=inputFF09_22, pattern="id.csv", recursive = TRUE)
#beep()

FF10<- list.files(path=inputFF10_22, pattern="id.csv", recursive = TRUE)
#beep()

FF11<- list.files(path=inputFF11_22, pattern="id.csv", recursive = TRUE)
#beep()



getwd()
# "\\\\largefile.nmbu.no/Project/FolloForest2021"

# [1] "FF1-CB/WAV_FF1-CB_06.09.2021_A/id.csv" "FF1-CB/WAV_FF1-CB_06.09.2021_B/id.csv" ...
# Slight gap between these so I need to manually reset the root directory for every site:( )


# #To read all your csv files and create a list with all these elements

## FF01
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF1")))
getwd()

FF01_data <- lapply(FF1, read.csv)

## FF02
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF2")))
getwd()

 FF02_data <- lapply(FF2, read.csv)

 ## FF03 
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF3")))
getwd()

 FF03_data <- lapply(FF3, read.csv)

 ## FF04
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF4")))
getwd()

 FF04_data <- lapply(FF4, read.csv)
 
## FF05
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF5")))
getwd()

 FF05_data <- lapply(FF5, read.csv)
 
## FF06
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF6")))
getwd()

 FF06_data <- lapply(FF6, read.csv)
 
## FF07
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF7")))
getwd()

 FF07_data <- lapply(FF7, read.csv)

 ## FF08
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF8")))
getwd() 

  FF08_data <- lapply(FF8, read.csv)

 ## FF09
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF9")))
getwd() 
 
  FF09_data <- lapply(FF9, read.csv)

 ## FF10
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF10")))
getwd() 

   FF10_data <- lapply(FF10, read.csv)

  ## FF11
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = setwd(rprojroot::find_rstudio_root_file( "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF11")))
getwd()   
   
 FF11_data <- lapply(FF11, read.csv)


  
#To add the name of each csv in the list
names(FF01_data) <- gsub("//.csv$", "", FF1)
names(FF02_data) <- gsub("//.csv$", "", FF2)
names(FF03_data) <- gsub("//.csv$", "", FF3)
names(FF04_data) <- gsub("//.csv$", "", FF4)
names(FF05_data) <- gsub("//.csv$", "", FF5)
names(FF06_data) <- gsub("//.csv$", "", FF6)
names(FF07_data) <- gsub("//.csv$", "", FF7)
names(FF08_data) <- gsub("//.csv$", "", FF8)
names(FF09_data) <- gsub("//.csv$", "", FF9)
names(FF10_data) <- gsub("//.csv$", "", FF10)
names(FF11_data) <- gsub("//.csv$", "", FF11)


#To create one single dataframe with all single dataframes
big_FF01<- rbindlist(FF01_data, fill = TRUE)
big_FF02<- rbindlist(FF02_data, fill = TRUE)
big_FF03<- rbindlist(FF03_data, fill = TRUE)
big_FF04<- rbindlist(FF04_data, fill = TRUE)
big_FF05<- rbindlist(FF05_data, fill = TRUE)
big_FF06<- rbindlist(FF06_data, fill = TRUE)
big_FF07<- rbindlist(FF07_data, fill = TRUE)
big_FF08<- rbindlist(FF08_data, fill = TRUE)
big_FF09<- rbindlist(FF09_data, fill = TRUE)
big_FF10<- rbindlist(FF10_data, fill = TRUE)
big_FF11<- rbindlist(FF11_data, fill = TRUE)



alist = list(big_FF01, big_FF02, big_FF03, big_FF04, big_FF05, big_FF06, big_FF07, big_FF08, big_FF09, big_FF10, big_FF11)

big_data <- rbindlist(alist, fill=TRUE)

setwd("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/RSummary_2022")

getwd()

#write.csv(big_data, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_unedited.csv")


# Explore where the NAs are coming from... 

big_data$AUTO.ID. <- as.factor(big_data$AUTO.ID.)
summary(big_data$AUTO.ID.)



big_FF04$AUTO.ID. <- as.factor(big_FF04$AUTO.ID.)
summary(big_FF04$AUTO.ID.) # 355 NAs from this site... mostly from the CB detector is seems... perhaps there was some issues with the microphone that resolved themselves.  
summary(big_FF04)
## I found another 8 NAs in FF-IB from the last day before the detector was collected. Could be there was a microphone failure or the detector had some other kind of issue. In any case, not much is lost and it does not appear to be a catastrophic failure. 

# In any case, it should be safe to remove these NAs. 
levels(big_data$AUTO.ID.)

big_data1 <- big_data %>% drop_na(AUTO.ID.) 
dim(big_data1)
# 483940     45
# 484304-483940 = 364 - GOOD!

# write.csv(big_data1, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA.csv")

# Remove the 261602 NOISE files as well. 

big_data2 <- big_data1 %>% filter(AUTO.ID. != "Noise") %>%  droplevels() 
summary(big_data2$AUTO.ID.)
dim(big_data2)
# 222338     45

#write.csv(big_data2, "2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise.csv")


```



## copying graveyard - things that did not work 

```{r, echo = F}
#J2 <- X2021_AutomaticallyProcessed_BatAcousticData_allsitescombined_dropNA_dropNoise_MREandNoIDandNyctalus_15_05_to_27_06 #38687 obs of 47 vars 
# Create new column with complete file directories using forward slashes 
#  J2$file.path <- gsub(pattern = ("\\"),
#                      replacement = "/",
#                      x = J2$OUTDIR,
#                      fixed = T)
#  head(J2$file.path) 
# # Not the complete file path unfortunately, another "FolloForest2021 folder needs to be included... 
# 
#   J2 <- mutate(J2, file.path1 = str_replace(file.path, "FolloForest2021", "FolloForest2021/FolloForest2021")) 
#  head(J2$file.path1)
# # 
# # # Create new column with complete file path
#   J2$full.file.path <- str_c(J2$file.path1, "/Data/", J2$OUT.FILE.FS) 
#  head(J2$full.file.path) 
# # 
# # # make a slightly shorter file path that is easier to process en masse
# # 
#  J2 <- mutate(J2, short.file.path = str_replace(full.file.path, "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/", ""))
#  head(J2$short.file.path)
# 
# # THIS can act like a file list. 
# my_files <- list(J2$short.file.path) # can be called when the working directory is up to BatAcousticData
# my_files1 <- list(J2$full.file.path)
# # 
# head(J2$full.file.path)
# 
# # Change working directory to make the file path name as short as possible while still being able to run the list.files function... 
# 
# setwd("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData")
# getwd() 
# # //largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF1/FF1-CB/WAV_FF1-CB_06.09.2021_A/Data
# path1 <- "/largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/"
# head(J2$full.file.path)
# # If this is the working directory, then the file path name can be
# 
# test.file <- "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/FF1/FF1-CB/WAV_FF1-CB_30.06.2021/Data/S4U12331_20210530_011033_000.wav"
# 
# file.copy(from = test.file, 
#           to = paste0(
# "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/ForJenn/", "S4U12331_20210530_011033_000.wav"))  
# 
# file.copy(from = paste0("//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/", my_files), 
#           to = paste0(
# "//largefile.nmbu.no/Project/FolloForest2021/FolloForest2021/Processed_Data/BatAcousticData/ForJenn", my_files))

```
